Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2015-05-18 msc-publication.tex
try splitting table into two tables

@@

\begin{table*}[t]
	\caption{Minimum and maximum tracer magnitudes and \(\ell^2\) error norms at \(t = \SI{10000}{\second}\) in the horizontal and terrain following tracer advection tests using centred linear and cubic upwind-biased schemes.}
\label{tab:advection}
%
\centering
\footnotesize
\begin{tabular}{ r @{\hspace{1.0em}} l @{\hspace{1.0em}} l @{\hspace{1.0em}} l | l @{\hspace{1.0em}} l @{\hspace{1.0em}} l | l @{\hspace{1.0em}} l @{\hspace{1.0em}} l | l @{\hspace{1.0em}} l @{\hspace{1.0em}} l}
\hline\hline
& \multicolumn{6}{c}{Horizontal advection} & \multicolumn{6}{c}{Terrain following advection} \\
& \multicolumn{3}{c}{Centred linear} & \multicolumn{3}{c}{Cubic upwind-biased} & \multicolumn{3}{c}{Centred linear} & \multicolumn{3}{c}{Cubic upwind-biased} \\
& \(\ell^2\) error & min & max & \(\ell^2\) error & min & max & \(\ell^2\) error & min & max & \(\ell^2\) error & min & max \\
\hline
Analytic   & 0 & 0 & 1 & 0 & 0 & 1 & 0 & 0 & 1 & 0 & 0 & 1 \\
% 	     l2		     min	     max	   l2		    min		     max           l2                        min                       max          l2                         min                       max
BTF 	   & \num{0.0210}  & \num{-0.275}  & \num{0.925} & \num{0.00791}  & \num{-0.0446}  & \num{0.925} & \num{0.00251}           & \num{-0.0245}           & \num{0.985} & \num{0.00154}           & \num{-0.0110}           & \num{0.983} \\
SLEVE      & \num{0.00233} & \num{-0.0252} & \num{0.985} & \num{0.00108}  & \num{-0.0106}  & \num{0.982} & \num{0.0173}            & \num{-0.120}            & \num{0.950} & \num{0.0120}            & \num{-0.0263}           & \num{0.865} \\
Cut cell   & \num{0.00224} & \num{-0.0251} & \num{0.985} & \num{0.000577} & \num{-0.00674} & \num{0.983} & \num{13.6}              & \num{-623}              & \num{3480}  & \num{0.0134}            & \num{-0.028}            & \num{0.851} \\
No terrain & \num{0.00223} & \num{-0.0251} & \num{0.985} & \num{0.000576} & \num{-0.00674} & \num{0.983} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & {---}       & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\
\hline
\end{tabular}
\end{table*}

>>>>

\begin{table*}[t]
	\caption{Minimum and maximum tracer magnitudes and \(\ell^2\) error norms at \(t = \SI{10000}{\second}\) in the horizontal tracer advection tests using centred linear and cubic upwind-biased schemes, and the fourth order scheme from \citet{schaer2002}.}
\label{tab:advection}
%
\centering
\footnotesize
\begin{tabular}{ r @{\hspace{1.0em}} l @{\hspace{1.0em}} l @{\hspace{1.0em}} l l @{\hspace{1.0em}} l @{\hspace{1.0em}} l}
\hline\hline
& \multicolumn{3}{c}{Centred linear} & \multicolumn{3}{c}{Cubic upwind-biased} \\
& \(\ell^2\) error & min & max & \(\ell^2\) error & min & max \\
\hline
Analytic   & 0 & 0 & 1 & 0 & 0 & 1 \\
% 	     l2		     min	     max	   l2		    min		     max        
BTF 	   & \num{0.0210}  & \num{-0.275}  & \num{0.925} & \num{0.00791}  & \num{-0.0446}  & \num{0.925} \\
SLEVE      & \num{0.00233} & \num{-0.0252} & \num{0.985} & \num{0.00108}  & \num{-0.0106}  & \num{0.982} \\
Cut cell   & \num{0.00224} & \num{-0.0251} & \num{0.985} & \num{0.000577} & \num{-0.00674} & \num{0.983} \\
No terrain & \num{0.00223} & \num{-0.0251} & \num{0.985} & \num{0.000576} & \num{-0.00674} & \num{0.983} \\
\hline
\end{tabular}
\end{table*}

@@

\begin{table*}[t]
	\caption{Minimum and maximum tracer magnitudes and \(\ell^2\) error norms at \(t = \SI{10000}{\second}\) in the terrain following tracer advection test using centred linear and cubic upwind-biased schemes.}
\label{tab:advection}
%
\centering
\footnotesize
\begin{tabular}{ r @{\hspace{1.0em}} l @{\hspace{1.0em}} l @{\hspace{1.0em}} l l @{\hspace{1.0em}} l @{\hspace{1.0em}} l}
\hline\hline
& \multicolumn{3}{c}{Centred linear} & \multicolumn{3}{c}{Cubic upwind-biased} \\
& \(\ell^2\) error & min & max & \(\ell^2\) error & min & max \\
\hline
Analytic   & 0 & 0 & 1 & 0 & 0 & 1 \\
% 	     l2                        min                       max          l2                         min                       max
BTF 	   & \num{0.00251}           & \num{-0.0245}           & \num{0.985} & \num{0.00154}           & \num{-0.0110}           & \num{0.983} \\
SLEVE      & \num{0.0173}            & \num{-0.120}            & \num{0.950} & \num{0.0120}            & \num{-0.0263}           & \num{0.865} \\
Cut cell   & \num{13.6}              & \num{-623}              & \num{3480}  & \num{0.0134}            & \num{-0.028}            & \num{0.851} \\
\hline
\end{tabular}
\end{table*}
